---
title: "Parliament_Analysis"
author: "Wibnu Dickson"
date: "27 August 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('dplyr')
library('knitr')
```

```{r}
sansad = read.csv('D://Exploratory Data Analysis//Datasets//ClassWork//parliament.csv')
```
#Identify year wise total number of electors and voters? Also compute percentage of voters 

```{r}
total_electors = sansad %>% group_by(YEAR) %>% summarise(total_electors=sum(unique(ELECTORS),na.rm=T),total_voters=sum(VOTES),per_voters=total_voters*100/(total_electors)) %>% arrange(-total_electors)
kable(total_electors[1:10,])


```

#Identify year wise percentage of male and female candidates?

```{r}
sansad = sansad %>% mutate(male=ifelse(SEX=="M",1,0))
sansad = sansad %>% mutate(female=ifelse(SEX=="F",1,0))
malfem100 = sansad %>% group_by(YEAR) %>% summarise(male_sum=sum(male),female_sum=sum(female),per_male=male_sum*100/(male_sum+female_sum),per_female=female_sum*100/(male_sum+female_sum)) %>% arrange(-YEAR)
kable(malfem100[1:10,])
```

#Compute party wise total number of candidates won so far? Display top ten parties alone

```{r}
sansad = sansad %>% mutate(win_cand=ifelse(Position==1,1,0))
party_won = sansad %>% group_by(PARTY) %>% summarise(win_cand1=sum(win_cand),) %>% arrange(-win_cand1)
kable(party_won[1:10,])
View(party_won)
```



#Identify year wise which party has won (based upon total number constituencies won)

```{r}
party_year_won = sansad %>% filter(Position==1)%>% group_by(YEAR,PARTY,add=T) %>% summarise(total_const=sum(win_cand)) %>% filter(total_const==max(total_const))
kable(party_year_won[1:10,])
```


#Identify year wise percentage of winning for female candidates?

```{r}
sansad = sansad %>% mutate(fem_win_cand=ifelse(win_cand==1 & female == 1,1,0))
sansad = sansad %>% mutate(mal_win_cand=ifelse(win_cand==1 & male==1,1,0))
win_fem_cand = sansad %>% group_by(YEAR) %>% summarise(male_win=sum(mal_win_cand),fem_win=sum(fem_win_cand),fem_per=fem_win*100/(fem_win+ male_win)) %>% arrange(-fem_per)
kable(win_fem_cand[1:10,])
```


